---
title: "LDM_HW2"
author: "2019313106 Hyungyeong Hong"
date: "5/20/2021"
output: html_document
---

### Part 1. Basic Settings  

Loading required packages  
```{r, message = FALSE}
library(tidyverse)
library(gcookbook)
```

Loading heightweight data from gcookbook library  
```{r}
data = heightweight
data %>% head(10)
```

### Part 2. Preprocessing Data  
Generating BMI column  
```{r}
data <- data %>% mutate(BMI = (weightLb / heightIn^2) * 703)
data %>% head(10)
```

Generating ageGroup column for further grouping with respect to ageMonth column  
Following the range in the given plot  
```{r}
data <- data %>%  mutate(
          ageGroup = ifelse(ageMonth < 145, "<145",
                            ifelse(ageMonth >= 145 & ageMonth < 155, "[145,155)", ">=155"))
)
data %>% head(10)
```

Grouping the data into three different age groups (by using ageMonth column)  
```{r}
data <- data %>% group_by(ageGroup)
```

### Part 3. Visualization  
Visualizing the data by using ggplot2 library  
```{r, fig.height = 5, fig.width = 5}
plt1 <- data %>% ggplot(aes(x = ageGroup, y = BMI, fill = sex)) +
  geom_boxplot(alpha = 0.6)

plt2 <- plt1 + 
  ggtitle("HW 2 Figure") +
  xlab("Age Group") +
  ylab("BMI")

plt3 <- plt2 +
  theme_minimal() +
  theme(
    plot.title = element_text(color = "darkgray", size = 20, face = "bold"),
    axis.title  = element_text(color = "darkgray", size = 15, face = "bold"),
    axis.text.x  = element_text(color = "gray"),
    axis.text.y  = element_text(color = "gray", angle = 90)
  )

plt4 <- plt3 +
  coord_flip() +
  scale_x_discrete(limits = c("<145", "[145,155)", ">=155"))

plt_5 <- plt4 +
  labs(fill = "Sex") +
  scale_fill_brewer(labels = c("Female", "Male"), palette = "Set1") +
  theme(legend.position = c(0.9, 0.15),
        legend.background = element_blank(),
        legend.title = element_text(color = "darkgray", face = "bold"),
        legend.text = element_text(color = "gray"))

plt_5
```

