---
title: "Analysis on Crimes of New York City"
author: "2019313106 홍현경"
date: "4/21/2021"
output:
  html_document:
    df_print: paged
---



loading packages
```{r message=FALSE}
library(tidyverse)
library(data.table)
```

changing working directory
```{r echo = FALSE}
setwd("/Users/hyungyeonghong/Desktop/LDM_project")
```

reading files
```{r settings_files, message=FALSE}
complaint_historic <- fread("NYPD_Complaint_Data_Historic.csv")
complaint_current <- fread("NYPD_Complaint_Data_Current.csv")
covid_nyc <- fread("NYC_covid19_cases.csv")
covid_us <- fread("COVID-19_Case_Surveillance_Public_Use_Data.csv")
```
  
Checking the Dimension of Each Data
```{r}
complaint_historic %>% dim
complaint_current %>% dim
```

Sorting the variable names of complaint_historic dataset and getting the number of variables
```{r}
complaint_historic %>% colnames %>% sort %>% print %>% length
```

Sorting the variable names of complaint_historic dataset and getting the number of variables
```{r}
complaint_current %>% colnames %>% sort %>% print %>% length
```

The variable "New Georeferenced Column" is deleted.
```{r}
complaint_current <- complaint_current %>% select(-`New Georeferenced Column`)
complaint_current %>% colnames %>% sort %>% print %>% length
```

Selecting the variables of complaint_historic data
```{r}
complaint_historic <-
  complaint_historic[, .(ADDR_PCT_CD, BORO_NM, CMPLNT_FR_DT, CMPLNT_FR_TM, CRM_ATPT_CPTD_CD, LAW_CAT_CD, OFNS_DESC, PD_DESC, PREM_TYP_DESC, SUSP_AGE_GROUP, SUSP_RACE, SUSP_SEX, VIC_AGE_GROUP, VIC_RACE, VIC_SEX, Latitude, Longitude)]

complaint_historic %>% dim # Checking the number of variables
```

Selecting the variables of complaint_current data
```{r}
complaint_current <-
  complaint_current[, .(ADDR_PCT_CD, BORO_NM, CMPLNT_FR_DT, CMPLNT_FR_TM, CRM_ATPT_CPTD_CD, LAW_CAT_CD, OFNS_DESC, PD_DESC, PREM_TYP_DESC, SUSP_AGE_GROUP, SUSP_RACE, SUSP_SEX, VIC_AGE_GROUP, VIC_RACE, VIC_SEX, Latitude, Longitude)]

complaint_current %>% dim # Checking the number of variables
```

Setting the modified variable names for each dataset
```{r}
original_varnames <- c("ADDR_PCT_CD", "BORO_NM", "CMPLNT_FR_DT", "CMPLNT_FR_TM", "CRM_ATPT_CPTD_CD", "LAW_CAT_CD", "OFNS_DESC", "PD_DESC", "PREM_TYP_DESC", "SUSP_AGE_GROUP", "SUSP_RACE", "SUSP_SEX", "VIC_AGE_GROUP", "VIC_RACE", "VIC_SEX", "Latitude", "Longitude")

modified_varnames <- c("precinct", "borough", "date", "time", "consequence", "level", "description", "granular_description", "premises", "suspect_age", "suspect_race", "suspect_sex", "victim_age", "victim_race", "victim_sex", "latitude", "longitude")
```

Changing the column names of complaint_historic dataset
```{r}
complaint_historic <- complaint_historic %>% setnames(original_varnames, modified_varnames)
complaint_historic %>% colnames # Checking the modified variable names
```

Changing the column names of complaint_current dataset
```{r}
complaint_current <- complaint_current %>% setnames(original_varnames, modified_varnames)
complaint_current %>% colnames
```

Checking the number of empty values in each column(variable) of complaint_historic dataset.
```{r}
(complaint_historic=="") %>% colSums(na.rm = TRUE)
```

These empty values are changed to NA's.
```{r}
historic_empty <- (complaint_historic == "")
```

```{r}
for(i in 1:ncol(complaint_historic)){
  colname <- colnames(complaint_historic)[i]
  idx <- which(historic_empty[,colname] == TRUE)
  complaint_historic[idx,colname] <- NA
}
```

```{r}
(complaint_historic=="") %>% colSums(na.rm = TRUE)
```


Checking the number of empty values in each column(variable) of complaint_current dataset.
```{r}
(complaint_current=="") %>% colSums(na.rm = TRUE)
```

These empty values are changed to NA's
```{r}
current_empty <- (complaint_current == "")
```

```{r}
for(i in 1:ncol(complaint_current)){
  colname <- colnames(complaint_current)[i]
  idx <- which(current_empty[,colname] == TRUE)
  complaint_current[idx,colname] <- NA
}
```

```{r}
(complaint_current=="") %>% colSums(na.rm = TRUE)
```

Checking the number of missing values in complaint_historic dataset
```{r}
complaint_historic %>% lapply(is.na) %>% sapply(sum)
```

Checking the number of missing values in complaint_current dataset
```{r}
complaint_current %>% lapply(is.na) %>% sapply(sum)
```


Checking the unique values of each variables in complaint_historic dataset
```{r ,results = 'hide'}
complaint_historic[,-c("date", "time", "latitude", "longitude")] %>% lapply(unique) %>% lapply(sort)
```

Checking the unique values of each variables in complaint_current dataset
```{r , results = 'hide'}
complaint_current[,-c("date", "time", "latitude", "longitude")] %>% lapply(unique) %>% lapply(sort)
```

Comparing the unique values of each variable
**borough**
```{r}
complaint_historic %>% 
  anti_join(complaint_current, by="borough") %>% 
  count(borough, sort=TRUE)
```

```{r}
complaint_current %>% 
  anti_join(complaint_historic, by="borough") %>% 
  count(borough, sort=TRUE)
```

**consequence**
```{r}
complaint_historic %>% 
  anti_join(complaint_current, by="consequence") %>% 
  count(consequence, sort=TRUE)
```

```{r}
complaint_current %>% 
  anti_join(complaint_historic, by="consequence") %>% 
  count(consequence, sort=TRUE)
```

**level**
```{r}
complaint_historic %>% 
  anti_join(complaint_current, by="level") %>% 
  count(level, sort=TRUE)
```

```{r}
complaint_current %>% 
  anti_join(complaint_historic, by="level") %>% 
  count(level, sort=TRUE)
```

**description**
```{r}
complaint_historic %>% 
  anti_join(complaint_current, by="description") %>% 
  count(description, sort=TRUE)
```

```{r}
complaint_current %>% 
  anti_join(complaint_historic, by="description") %>% 
  count(description, sort=TRUE)
```

**granular_description**
```{r}
complaint_historic %>% 
  anti_join(complaint_current, by = "granular_description") %>% 
  count(granular_description, sort = TRUE)
```

```{r}
complaint_current %>% 
  anti_join(complaint_historic, by = "granular_description") %>% 
  count(granular_description, sort = TRUE)
```
**suspect_race**
```{r}
complaint_historic %>% 
  anti_join(complaint_current, by="suspect_race") %>% 
  count(suspect_race, sort=TRUE)
```

```{r}
complaint_current %>% 
  anti_join(complaint_historic, by="suspect_race") %>% 
  count(suspect_race, sort=TRUE)
```

**suspect_sex**
```{r}
complaint_historic %>% 
  anti_join(complaint_current, by="suspect_sex") %>% 
  count(suspect_sex, sort=TRUE)
```

```{r}
complaint_current %>% 
  anti_join(complaint_historic, by="suspect_sex") %>% 
  count(suspect_sex, sort=TRUE)
```

**victim_race**
```{r}
complaint_historic %>% 
  anti_join(complaint_current, by="victim_race") %>% 
  count(victim_race, sort=TRUE)
```

```{r}
complaint_current %>% 
  anti_join(complaint_historic, by="victim_race") %>% 
  count(victim_race, sort=TRUE)
```

**victim_sex**
```{r}
complaint_historic %>% 
  anti_join(complaint_current, by="victim_sex") %>% 
  count(victim_sex, sort=TRUE)
```

```{r}
complaint_current %>% 
  anti_join(complaint_historic, by="victim_sex") %>% 
  count(victim_sex, sort=TRUE)
```

**date**        
Checking the unique values of date in complaint_historic data
```{r}
complaint_historic$date %>% unique %>% length
```

**[Year]**
```{r}
historic_years <- complaint_historic$date %>% str_sub(7, 10) %>% as.numeric
historic_years %>% unique %>% sort(decreasing=TRUE)
```

These are invalid years, and therefore should be deleted
```{r}
historic_years_invalid <- which(historic_years < 2006)
```

**[Month]**
```{r}
complaint_historic$date %>% str_sub(1, 2) %>% as.numeric %>% unique %>% sort
```
  
**[Day]**
```{r}
complaint_historic$date %>% str_sub(4, 5) %>% as.numeric %>% unique %>% sort
```
  
Checking the unique values of date in complaint_current data
```{r}
complaint_current$date %>% unique %>% length
```

**[Year]**
```{r}
current_years <- complaint_current$date %>% str_sub(7, 10) %>% as.numeric
current_years %>% unique %>% sort(decreasing=TRUE)
```
  
These are invalid years, and therefore should be deleted
```{r}
current_years_invalid <- which(current_years != 2020)
```

**[Month]**
```{r}
complaint_current$date %>% str_sub(1, 2) %>% as.numeric %>% unique %>% sort
```
  
**[Day]**
```{r}
complaint_current$date %>% str_sub(4, 5) %>% as.numeric %>% unique %>% sort
```

Deleting the rows of complaint_historic data with invalid years
```{r}
complaint_historic <- complaint_historic[-historic_years_invalid, ]
complaint_historic %>% dim
```

Deleting the rows of current_historic data with invalid years
```{r}
complaint_current <- complaint_current[-current_years_invalid, ]
complaint_current %>% dim
```

**precinct**    
Checking the unique values in precinct variable in complaint_historic dataset
```{r}
complaint_historic$precinct %>% unique %>% sort
```

However, -99 precinct doesn't exist and therefore this value should be changed to NA.
```{r}
precinct_invalid <- which(complaint_current$precinct == -99)
```

```{r}
complaint_historic$precinct[precinct_invalid] <- NA
```

Checking the unique values in precinct variable in complaint_current dataset
```{r}
complaint_current$precinct %>% unique %>% sort
```

**time**    
Checking the unique values in time variable in complaint_historic dataset

**[Hour]**
```{r}
complaint_historic$time %>% str_sub(1, 2) %>% as.numeric %>% unique %>% sort
```

**[Minute]**
```{r}
complaint_historic$time %>% str_sub(4, 5) %>% as.numeric %>% unique %>% sort
```

**[Second]**
```{r}
complaint_historic$time %>% str_sub(7, 8) %>% as.numeric %>% unique %>% sort
```

Checking the unique values in time variable in complaint_current dataset
**[Hour]**
```{r}
complaint_current$time %>% str_sub(1, 2) %>% as.numeric %>% unique %>% sort
```

**[Minute]**
```{r}
complaint_current$time %>% str_sub(4, 5) %>% as.numeric %>% unique %>% sort
```

**[Second]**
```{r}
complaint_current$time %>% str_sub(7, 8) %>% as.numeric %>% unique %>% sort
```

**victim_age**
Checking the unique values in victim_age variable in complaint_current dataset
```{r}
complaint_historic$victim_age %>% unique %>% sort
```

* Adequate range of age: "<18", "18-24", "25-44", "45-64", "65+"
* Therefore, victim_age values that do not match with these values should be changed to NA's.
```{r}
victim_age_invalid <- which((complaint_historic$victim_age != "<18") & (complaint_historic$victim_age != "18-24") & (complaint_historic$victim_age != "25-44") & (complaint_historic$victim_age != "45-64") & (complaint_historic$victim_age != "65+"))
```

```{r}
complaint_historic$victim_age[victim_age_invalid] <- NA
```

```{r}
complaint_historic$victim_age %>% unique %>% sort
```


Also changing victim_age values in complaint_current dataset that are out of range
```{r}
victim_age_invalid <- which((complaint_current$victim_age != "<18") & (complaint_current$victim_age != "18-24") & (complaint_current$victim_age != "25-44") & (complaint_current$victim_age != "45-64") & (complaint_current$victim_age != "65+"))
```

```{r}
complaint_current$victim_age[victim_age_invalid] <- NA
```

```{r}
complaint_current$victim_age %>% unique %>% sort
```

**suspect_age**
Changing suspect_age values in complaint_historic dataset that are out of range
```{r}
suspect_age_invalid <- which((complaint_historic$suspect_age != "<18") & (complaint_historic$suspect_age != "18-24") & (complaint_historic$suspect_age != "25-44") & (complaint_historic$suspect_age != "45-64") & (complaint_historic$suspect_age != "65+"))
```

```{r}
complaint_historic$suspect_age[suspect_age_invalid] <- NA
```

```{r}
complaint_historic$suspect_age %>% unique %>% sort
```


* Changing suspect_age values in complaint_current dataset that are out of range
```{r}
suspect_age_invalid <- which((complaint_current$suspect_age != "<18") & (complaint_current$suspect_age != "18-24") & (complaint_current$suspect_age != "25-44") & (complaint_current$suspect_age != "45-64") & (complaint_current$suspect_age != "65+"))
```

```{r}
complaint_current$suspect_age[suspect_age_invalid] <- NA
```

```{r}
complaint_current$suspect_age %>% unique %>% sort
```

**latitude**
Checking the range of latitude variable values in complaint_historic dataset
```{r}
complaint_historic$latitude %>% range(na.rm = TRUE)
```
The maximum value does not belong to the latitude of New York City  

The minimum values, the 1st quartile, median, the 3rd quartile and the maximum value should be checked to detect possible mistaken values  
```{r}
complaint_historic$latitude %>% summary
```
The latitude values of these observations are possible mistaken values   
However, these values are not going to be changed to NA's   
They are going to be detected as obvious  mistaken values when we plot the latitude and longitude values on the map    
Therefore, these values are going to be handled on visualization section   
```{r}
complaint_historic[latitude >= 41]
```

Checking the range of latitude variable values in complaint_current dataset
```{r}
complaint_current$latitude %>% range(na.rm = TRUE)
```
The range above matches the latitude of New York City  
Latitude values will be further investigated in visualization section  

**longitude**
Checking the range of longitude variable values in complaint_historic dataset
```{r}
complaint_historic$longitude %>% range(na.rm = TRUE)
```
The minimum value does not belong to the longitude of New York City  
The minimum values, the 1st quartile, median, the 3rd quartile and the maximum value should be checked to detect possible mistaken values  
```{r}
complaint_historic$longitude %>% summary
```
The longitude values of these observations are possible mistaken values  
However, these values are not going to be changed to NA's since it's not obvious whether they are mistaken or not  
They are going to be detected as obvious mistaken values when we plot the latitude and longitude values on the map   
Therefore, these values are going to be handled on visualization section  
```{r}
complaint_historic[longitude <= -75]
```

Checking the range of longitude variable values in complaint_current dataset
```{r}
complaint_current$longitude %>% range(na.rm = TRUE)
```
The range above matches the longitude of New York City  
Longitude values will be further investigated in visualization section   


Binding the two data sets and making them into a single dataset  
```{r}
complaint_data <- rbind(complaint_historic, complaint_current)
```

* Checking the dimension of combined dataset
```{r}
complaint_data %>% dim
```

Changing the format of the values: from character to date  
```{r}
# lubridate is not working
# data.table format is also not working due to an error
complaint_data$date <- complaint_data$date %>%
  str_replace("([0-9]{2})/([0-9]{2})/(20[0-9]{2})", "\\3-\\1-\\2")
complaint_data$date <- complaint_data$date %>% as.Date
complaint_data %>% head(10)
```

Sorting the data by date in an increasing order
```{r}
complaint_data <- complaint_data[order(date),]
```

Checking the last date of the data set
```{r}
complaint_data[order(-date)][1, date]
```
Therefore, the final date of integrated data is going to be 2020-12-31  

Data EDA / Preprocessing: New York City COVID-19 Cases  

Checking the Dimension of the Dataset
```{r}
covid_nyc %>% dim
```

Checking the variable(column) names of the dataset
```{r}
covid_nyc %>% colnames
```

Since we are interested in daily COVID-19 status, date_of_interest, CASE_COUNT and DEATH_COUNT variables are selected  
PROBABLE_CASE_COUNT and PROBABLE_DEATH_COUNT variables contain the positive cases with positive antigen test result. However, CSTE updated the position statement on August 5, 2020 to clarify the interpretation of antigen detection tests and serologic test results within the case classification. Therefore those two variables are not selected  
```{r}
covid_nyc <- covid_nyc %>% select(date_of_interest, CASE_COUNT, DEATH_COUNT)
```

Changing variable names for better readability
```{r}
covid_nyc <- covid_nyc %>% rename(date = date_of_interest,
                                  nyc_cases = CASE_COUNT, nyc_deaths = DEATH_COUNT)
```

Checking the number of missing values
```{r}
covid_nyc %>% lapply(is.na) %>% sapply(sum)
```
There are no missing values in the dataset   

Changing the format of date values  
covid_nyc dataset is going to be joined with complaint_data with respect to date variable  
Therefore, date value format of covid_nyc is changed in order to unify the format with date value format of complaint_data  
```{r}
covid_nyc$date <- covid_nyc$date %>%
  str_replace("([0-9]{2})/([0-9]{2})/(20[0-9]{2})", "\\3-\\1-\\2")
covid_nyc$date <- covid_nyc$date %>% as.Date
covid_nyc %>% head(10)
```

Data EDA / Preprocessing: US COVID-19 Cases  

Checking the Dimension of the Dataset  
```{r}
covid_us %>% dim
```

Deleting unnecessary variables  
Checking the variable(column) names of the dataset  
```{r}
covid_us %>% colnames
```

Since we are interested in daily COVID-19 status, cdc_case_earliest_dt and death_yn variables are selected  
CDC recommends researchers use cdc_case_earliest_dt in time series and other analysis  
We are going to keep cdc_case_earliest_dt variable, which indicates confirmed date, and group the data with this variable  
Therefore the name of cdc_case_earliest_dt is changed to "date" for better readability and convenience of further analysis  
```{r}
covid_us <- covid_us %>% select(date = cdc_case_earliest_dt, death_yn)
```

Creating a Table with Daily Cases  
To get the daily number of cases, the dataset is grouped by date variable, and then the number of cases are counted for each date value  
```{r}
covid_us_cases <- covid_us %>% group_by(date) %>% 
  summarise(us_cases = n())
```

To get the daily number of deaths, the dataset is grouped by date variable and death_yn variable, and then the number of deaths are counted for each combination of the variable values.  
Since we are only interested in the number of deaths in each day, only the rows with death_yn value "Yes" is filtered.  
death_yn indicates death status(Did the patient die due to the illness?)  
It has total 4 values; Yes, No, Unknown and Missing  
```{r, message = FALSE}
covid_us_deaths <- covid_us %>% group_by(date, death_yn) %>% 
  summarise(us_deaths = n()) %>% filter(death_yn == "Yes") %>% 
  select(date, us_deaths)
```

covid_us_cases has more rows and therefore covid_us_cases and covid_us_deaths are left-joined   
```{r, message = FALSE}
covid_us <- left_join(covid_us_cases, covid_us_deaths, by = "date")
covid_us
```

Checking missing values  
Checking the number of missing values in the joined table  
```{r}
covid_us %>% lapply(is.na) %>% sapply(sum)
```

There are three missing values in us_deaths variable  
NA means no death (NA was generated since there were no such dates in covid_us_deaths table)  
Therefore NA's are changed to 0  
```{r}
covid_us %>% replace_na(list(us_deaths = 0))
```

Changing the format of date values  
covid_us dataset is going to be joined with complaint_data with respect to date variable  
Therefore, date value format of covid_us is changed in order to unify the format with date value format of complaint_data  
```{r}
covid_us$date <- covid_us$date %>%
  str_replace("([0-9]{2})/([0-9]{2})/(20[0-9]{2})", "\\3-\\1-\\2")
covid_us$date <- covid_us$date %>% as.Date
covid_us %>% head(10)
```

Data EDA / Preprocessing: Integrating the Datasets  
Left joining complaint_data and covid_nyc datasets  
```{r, message = FALSE}
data <- left_join(complaint_data, covid_nyc, by = "date")
```

Left joining the integrated dataset and covid_us dataset
```{r, message = FALSE}
data <- left_join(data, covid_us, by = "date")
```

Checking the final data  
Final data table  
```{r}
data
```

Checking the last date  
```{r}
data$date %>% max(na.rm = TRUE)
```
This is valid since the last date of date in complaint_data is 2020-12-31  

```{r}
data %>% write.csv("data_preprocessed.csv")
```

```{r}
preprocessed_data <- fread("data_preprocessed.csv")
```

```{r}
preprocessed_data
```

```{r}
preprocessed_data <- preprocessed_data %>% select(-V1)
```

```{r}
preprocessed_data
```

